Calendar-based graphics for visualizing people's daily schedules

### 2018-10-08 main.Rmd
swapped x and y in the lagged scatterplot

\newpage

```
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
               sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
               scale = "fixed", width = 0.95, height = 0.95)
```

@@

The \code{frame\_calendar} function is not constrained to line plots. The full range of plotting capabilities in \pkg{ggplot2} is essentially available. Figure \ref{fig:scatterplot} shows a lag scatterplot at Flinders Street Station, where the current hourly count is assigned to the \code{x} argument and the lagged hourly count to the \code{y} argument. This figure is organized in the daily calendar layout. Figure \ref{fig:scatterplot} indicates two primary patterns, strong autocorrelation on weekends, and weaker autocorrelation on work days. At the higher counts, on week days, the next hour sees possibly substantial increase or decrease in counts, essentially revealing a bimodal distribution of consecutive counts, as supported by Figure \ref{fig:flinders-2016}.

```{r scatterplot, fig.height = 5, fig.cap = "Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days."}
```

@@

>>>>

```
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95
)
```

@@

The \code{frame\_calendar} function is not constrained to line plots. The full range of plotting capabilities in \pkg{ggplot2} is essentially available. Figure \ref{fig:scatterplot} shows a lag scatterplot at Flinders Street Station, where the lagged hourly count is assigned to the \code{x} argument and the current hourly count to the \code{y} argument. This figure is organized in the daily calendar layout. Figure \ref{fig:scatterplot} indicates two primary patterns, strong autocorrelation on weekends, and weaker autocorrelation on work days. At the higher counts, on week days, the next hour sees possibly substantial increase or decrease in counts, essentially revealing a bimodal distribution of consecutive counts, as supported by Figure \ref{fig:flinders-2016}.

```{r scatterplot, fig.height = 5, fig.cap = "Lag scatterplot in the daily calendar layout. Each hour's count is plotted against previous hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days."}
```

@@

# Bibliography

### 2018-10-08 main.tex
swapped x and y in the lagged scatterplot

\newpage

\begin{verbatim}
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
               sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
               scale = "fixed", width = 0.95, height = 0.95)
\end{verbatim}

@@

The \code{frame\_calendar} function is not constrained to line plots.
The full range of plotting capabilities in \pkg{ggplot2} is essentially
available. Figure \ref{fig:scatterplot} shows a lag scatterplot at
Flinders Street Station, where the current hourly count is assigned to
the \code{x} argument and the lagged hourly count to the \code{y}
argument. This figure is organized in the daily calendar layout. Figure
\ref{fig:scatterplot} indicates two primary patterns, strong
autocorrelation on weekends, and weaker autocorrelation on work days. At
the higher counts, on week days, the next hour sees possibly substantial
increase or decrease in counts, essentially revealing a bimodal
distribution of consecutive counts, as supported by Figure
\ref{fig:flinders-2016}.

@@

\caption[Lag scatterplot in the daily calendar layout]{Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{Schunk}

@@

>>>>

\begin{verbatim}
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95
)
\end{verbatim}

@@

The \code{frame\_calendar} function is not constrained to line plots.
The full range of plotting capabilities in \pkg{ggplot2} is essentially
available. Figure \ref{fig:scatterplot} shows a lag scatterplot at
Flinders Street Station, where the lagged hourly count is assigned to
the \code{x} argument and the current hourly count to the \code{y}
argument. This figure is organized in the daily calendar layout. Figure
\ref{fig:scatterplot} indicates two primary patterns, strong
autocorrelation on weekends, and weaker autocorrelation on work days. At
the higher counts, on week days, the next hour sees possibly substantial
increase or decrease in counts, essentially revealing a bimodal
distribution of consecutive counts, as supported by Figure
\ref{fig:flinders-2016}.

@@

\caption[Lag scatterplot in the daily calendar layout]{Lag scatterplot in the daily calendar layout. Each hour's count is plotted against previous hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{Schunk}

@@

\hypertarget{bibliography}{%
\section*{Bibliography}\label{bibliography}}
\addcontentsline{toc}{section}{Bibliography}
